Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-04-11 presentation/presentation.tex
added the multipayload optimization stuff
Merged conflicts

\begin{frame}{Presentation Guidelines}

You will sign up for a 10 minute presentation time slot. The presentation is graded only for completion. Group projects will have 8 minutes to present and 2 minutes for Q\&A. Individuals will have 6 minutes to present and 2 minutes for Q\&A. Obviously you will not have a lot of time to spend on details. Instead, you should focus on motivation (what the problem is and why it is important), the solution approach, and the most important results. Each member of the team should have a role in the presentation.

\begin{frame}{Outline}
\begin{itemize}
	\item{Motivation and Background}
	\item{---figure of multirotor trends in flight time}
	\item{---focus on OTS stuff bases our design on empirical models}

	\item{Theory - models}
	\item{---Engine model}
	\item{---Aero model}

	\item{Optimization}
	\item{---Objective only directly a function of 2 design variables}
	\item{---constraints}

	\item{Results}
	\item{lessons learned}
	\item{questions}
\end{itemize}
\end{frame}

@@

	What is a gas quad...
\end{frame}

@@

\begin{frame}{Models}
	\begin{itemize}
		\item{To represent the aerodynamics of each rotor, we used Combined Differential Blade Element and Momentum Theory for nonuniform inflow.}
		\begin{center}
		$$ dT = \frac{1}{2} \rho a \Omega^2 r^2 (\theta - \phi) c \  dr $$
		$$ dQ = \frac{1}{2} \rho \Omega^2 r^3 c (\delta + \phi C_L) \ dr $$
		\end{center}
	\end{itemize}

@@

\begin{frame}{Optimization Method}
	Design Variables
	\begin{itemize}
		\item{Engine Size}
		\item{Rotor Size}
		\item{Fuel Capacity}
		\item{Fuel Burn Rate}
		\item{theta hover}
		\item{omega}
	\end{itemize}

	Flight Time = f(Fuel Capacity/Fuel Rate)

	C = ...

	SNOPT
\end{frame}

@@

\begin{frame}{Lessons Learned}
	\begin{itemize}
		\item{Helicopter rotor dynamics are difficult to conceptualize and calculate.}
		\item{Over-simplification of aerodynamic model leads to unrealistic results.}
		\item{large, slow props - https://youtu.be/syJq10EQkog?t=7s}

	\end{itemize}
\end{frame}

>>>>

@@

	What is a gas multirotor?
	\begin{itemize}
	\item{Uses a single small two-stroke engine.}
	\item{Power is transfered through torque tubes to the rotors.}
	\item{All rotors must be variable pitch.}
	\item{Theoretically capable of longer flight times than battery powered multirotors because of higher specific energy of gasoline.}
	\end{itemize}
\end{frame}

@@

\begin{frame}{Aerodynamic Model}
	\begin{itemize}
		\item{To represent the aerodynamics of each rotor, we used Combined Differential Blade Element and Momentum Theory for nonuniform inflow.}
		\begin{center}
		$$ dT = \frac{1}{2} \rho a \Omega^2 r^2 (\theta - \phi) c \  dr $$
		$$ dQ = \frac{1}{2} \rho \Omega^2 r^3 c (\delta + \phi C_L) \ dr $$
		\end{center}
	\end{itemize}

@@

\begin{frame}{Optimization Method}
	Design Variables
	\begin{itemize}
		\item{Engine Size}
		\item{Rotor Size}
		\item{Fuel Capacity}
		\item{Fuel Burn Rate}
		\item{Rotor Pitch Angle}
		\item{Head Speed}
	\end{itemize}

	$Flight Time = f(Fuel Capacity, Fuel Rate)$

	$C: P_{Shaft} \geq P_{Rotor}, T \geq W_{total}, P_{max} \geq P_{Shaft}, 55lbs \geq W_{total} $

	SNOPT to optimize

@@

\begin{frame}{Results}
	Simultaneously optimize over 3, 5, and 7 kg payload
	\begin{itemize}
		\item{Engine Size: 177 cc} 
		\item{Rotor Size: 2.16 m}
		\item{Fuel Capacity: 6.45 kg}
		\item{Fuel Burn Rate: 0.0019 kg/s}
		\item{Rotor Pitch Angle: 17.618 deg}
		\item{Head Speed: 135.09 rpm}
	\end{itemize}

	Flight Time > 42.47 minutes

	Payload < 7 kg
\end{frame}

\begin{frame}{Lessons Learned}
	\begin{itemize}
		\item{Large, Slow props - https://youtu.be/syJq10EQkog?t=7s}
		\item{Helicopter rotor dynamics are difficult to conceptualize and calculate.}
		\item{Over-simplification of aerodynamic model leads to unrealistic results.}
		\item{Scaling the problem was critical}	
	\end{itemize}
\end{frame}
